### 2012-02-13 paper.tex
Minor corrections

\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams. A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction. Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active (under-coordinated?) sites.

Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure. It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{Reactor}
The experiments were performed in silicon-based 20x15 mm $\mu$-reactors \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.

@@

The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.

\subsection{Platinum nanoparticle deposition}
Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\,\% platinum target in a magnetron sputter source. After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio. Using this setup platinum nanoparticles with diameters in the range of 2–16 nm can be produced \cite{Nielsen2010,Nielsen2009}. The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor. The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition. After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial lightoff the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
  \label{fgr:full_oscillation}
\end{figure*}

Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations as a function of pressure. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_2$ pressure was observed. At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations is more irregular which as shown in Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

A very destinct temperature dependence is seen on the oscillation frequency, an example is given in Figure~\ref{fgr:temperature_dependence}. The exact magnitude is not completely consistent between samples, but the effect is always large. This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step, the oscillation period was apprixmately 500\,s, after the step, the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 did not produce any oscillations in our system. CO/O$_2$ ratios lower than 0.175 were needed to provoke oscillations in our system. This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures. The low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle. Once poisoned, an increase in temperature would be necessary to ignite the reaction again.

@@

Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence concluded that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette... 
It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.

%Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.

The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts}. This phenomena is consistent across all measured samples with approximately the oscillation period evolution with time. The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters. Skriv noget mere her...

>>>>

\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations tends to increase in with time while the duty cycle remains constant. Jeg synes, at vi skal skrive abstractet om. Det skal i alle være længere og mere præcist.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams. A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction. Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.

Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure. Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{Reactor}
The experiments were performed in silicon-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu m$ wide capillary used for sniffing gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.

@@

The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.

\subsection{Platinum nanoparticle deposition}
Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\% platinum target in a magnetron sputter source. After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio. Using this setup platinum nanoparticles with diameters in the range of 2–16 nm can be produced \cite{Nielsen2010,Nielsen2009}. The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor. The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition. After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial lightoff the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The qualitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples from 3\,nm to 9\,nm and in a wide coverage regime. A geometrical coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself. The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
  \label{fgr:full_oscillation}
\end{figure*}

The pressure dependence of the oscillations were also investigated. In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior with changing pressure. Similarly, only a weak dependence on the CO/O$_2$ pressure was observed. At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.

\section{Discussion}
This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.

The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 did not produce any oscillations in our system. This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures. The low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle. Once poisoned, an increase in temperature would be necessary to ignite the reaction again.

@@

Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.  It is hence concluded that the oscillations is a feature related to the catalyst. It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface. A detailed proposal for the reaction mechanism on Pd has been developed \cite{Hendriksen2010} and our data is consistent with this model. According to the proposed model, the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate. In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles. Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO. At a given point the CO concentration will become low enough that a light-off like phenomenon will set in and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters.

%This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.

\section{Conclusion}
We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry. We have shown oscillations wide range of sizes of nanoparticles and a large span i CO-concentration. Burde vi ikke skrive lidt mere om, hvad vi egentlig præsenter? Vi viser egentlig ikke så meget med størrelseafhængighed og CO-koncentrations-eksperimenter.
